SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2019-01-11 reports/si.tex
preprint2
update doi
si perfect

\begin{document}

\author{A.~R.~McCluskey}
\thanks{A.R.M. and A.S.-F. contributed equally to this work}
\email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}

@@

>>>>

\begin{document}
\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the
structure of lipid monolayers''}% Force line breaks with \\%
\author{A.~R.~McCluskey}
\thanks{A.R.M. and A.S.-F. contributed equally to this work}
\email{a.r.mccluskey@bath.ac.uk/andrew.mccluskey@diamond.ac.uk}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}

@@

This Supplementary Information document is only part of a fully reproducible analysis workflow. The complete workflow, along with all datasets, figure files, and analysis/plotting scripts is available at \url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.2538002) under a CC BY-SA 4.0 license.
